Web Processing - Standardised GIS Analyses for Cable Route Planning

### 2023-02-19 paper/methods.tex
added Supplement S1
paper:
results.tex:
added part for the sub-sections:
 1) for overlay of both rasterizations
 2) for down sampled cost paths

refactor: added discussion.tex
added citations, parts for the Introduction

update format of least_cost_path_evaluation.ipynb

\begin{table}[h!]
	\caption{Used levels of costs, the applied numerical equivalent and example layer this cost have been used for.}
	\label{tab:1}
	\centering
	\begin{tabular}{ l  r  l }
		Cost Level 			& Cost 					& Example\\
		\hline
		Prohibited 			& 500					& \makecell[lt]{Conversation areas as\\ National Parks, Buildings} \\
		strongly Restricted & 10 					& \makecell[lt]{Conversation areas as Bird Reserve} \\
		Restricted 			& 5						& \makecell[lt]{Protected Landscape Area,\\ Industrial Areas, motorway, railway} \\
		No Restriction 		& 0.5					& Default\\
		Preferential 		& 0.1					& \makecell[lt]{Power Grid,\\ Motorway and Railway Buffers}\\
	\end{tabular}
\end{table}
The completed list of layers and the processing applied to them, can be found in Supplement S1. \todo{create the Supplement from the processing rules}

>>>>

\begin{table}[h!]
	\caption{Used levels of costs, the applied numerical equivalent and example layer this cost have been used for.}
	\label{tab:1}
	\centering
	\begin{tabular}{ l  r  l }
		Cost Level 			& Cost 					& Example\\
		\hline
		Prohibited 			& 500					& \makecell[lt]{Conversation areas as\\ National Parks, Buildings} \\
		strongly Restricted & 10 					& \makecell[lt]{Conversation areas as Bird Reserve} \\
		Restricted 			& 5						& \makecell[lt]{Protected Landscape Area,\\ Industrial Areas, motorway, railway} \\
		No Restriction 		& 0.5					& Default\\
		Preferential 		& 0.1					& \makecell[lt]{Power Grid,\\ Motorway and Railway Buffers}\\
	\end{tabular}
\end{table}
The completed list of layers and the processing applied to them, can be found in \textbf{Supplement S1}.

The whole stack of the cost raster, via the aggregated costs to the resulting least cost path can is shown with an example for a starting cost raster of 50~m resolution and a rasterization with all touched False (see \ref{fig:costs2path}).
Because of the early stopping strategy used in the aggregation sub-paths with high costs have not been fully computed.
Instead, the execution stops early after reaching the end point.
Because the end point ends at a power transformer, which is a building type, the paths ends at in a Prohibited Area.
Therefore, areas even farther away from the starting point have been explored first.

\begin{figure}
	\centering

	\subfloat[\centering Cost Raster.]{{\includegraphics[width=.45\linewidth]{./images/CostRasterExample.png} }}%
	\qquad
	\subfloat[\centering Aggregated Cost Raster.]{{\includegraphics[width=.45\linewidth]{./images/AggregatedCosts.png} }}%
	\qquad
	\subfloat[\centering Least Cost Path.]{{\includegraphics[width=.45\linewidth]{./images/LeastCostPathExample.png} }}%

	\caption{Figures of Cost raster and the resulting aggregated Costs and the least cost path for a resolution of 50~m.}
	\label{fig:costs2path}
\end{figure}

### 2023-02-19 paper/paper-CableRoute.tex
added Supplement S1
paper:
results.tex:
added part for the sub-sections:
 1) for overlay of both rasterizations
 2) for down sampled cost paths

refactor: added discussion.tex
added citations, parts for the Introduction

update format of least_cost_path_evaluation.ipynb

	Sometimes, finding the shortest path is not sufficient.
	Additional parameters play also have to be taken into consideration.
	As the steepness of a road or the soil, play an important role for the building cost of a road or pipeline
	\todo{source}.
	For planing the additional routes for a power grid, additional aspects as legal regulations and acceptance
	by the local population have to be taken in consideration.
	Also technical aspects, as the effects on the grid stability might be further points to consider.\cite{schafer_understanding_2022}
	\todo{what is the least cost path}

	The aggregation is implemented in a priority queue. 
	Hence a point with a lower cost is evaluated earlier as a starting position to evaluate the cost of its neighbors, than a point with higher costs.
	The aggregation is implemented with early stopping. 
	After the last end point has been has got an aggregated cost the aggregation stops and the back tracking starts.

	\section{Methods}\label{sec:methods}
	\input{methods}

	\section{Results}\label{sec:results}
	\input{results}

	\section{Discussion}\label{sec:discussion}
	As shown need of computation power increases with the power of two with the resolution.
	While the error only scales linear with the resolution.

	As the original least cost path QGIS plug-in the used algorithm stops the least aggregation of the costs after the final end point has been found.
	This early stopping might result in sub optimal paths around the end points.

	As a any buffer around buildings are describes as protected areas, power poles are also included.
	In further works, these should be excluded.

	Difference aggregation of the rule of a cost raster with max vs sum

	Scaling with multiple endpoints.
	Not algorithmic speed-ups as precompilation, JIT, vector units, multi-core
	\section{Related Works}\label{sec:related-works}

	\section{Conclusion}\label{sec:conclusion}

>>>>

	Sometimes, finding the shortest path is not sufficient.
	Additional parameters also have to be taken into consideration.
	As the steepness of a road or the soil, play an important role for the building cost of a road or pipeline
	\cite{suleiman_optimal_2015}.
	For planing the additional routes for a power grid, additional aspects as legal regulations and acceptance
	by the local population have to be taken in consideration.
	Also technical aspects, as the effects on the grid stability might be further points to consider.\cite{schafer_understanding_2022}

	Due to the increasing need for renewable energy wind off shore wind turbines are source which currently supplies 5.5~\% annual percentage in 2020 of the German energy mix.~\cite{noauthor_nettostromerzeugung_2021}
	For wind energy in general highest efficiency can only be archived with high wind speeds. Highest wind speeds are reached along the cost lines in the north of Germany.
	In contrast, most consumers, as industry are situated in south Germany.
	Source and consumer have to be linked via new power lines.

	Other methods as the multi-criteria decision analysis take further aspects and stakeholder as experts, public and decision maker and into consideration.\cite{bertsch_participatory_2016}

	For planning a possible route for a power line the least cost path algorithm is applied.
	The least cost path algorithm is a Dijkstra algorithm applied on a raster map.
	The vertices of the graph are the centers on neighboring pixels in al possible eight directions.
	The weights of the edges are the local costs to travel from one pixel to the neighboring pixel.
	The costs might be physical costs, as the local slope, but also can be composed on other factors as the acceptance rate for the land usage of a given class.
	The least cost path algorithm consists of at least two sequential steps. 1) The first steps is to aggregate the costs of traveling from the starting point to a given set of end points. This steps generates the aggregated cost raster of the total cost that are needed to travel to a point, from the cost raster.
	2) In the next step the back tracking, the route of the actual least cost path is calculated. For each ending point the path via the lowest cost neighbor is taken until arriving at the starting point.

	\todo{Were to put the following part?}
	The aggregation is implemented in a priority queue. 
	Hence a point with a lower cost is evaluated earlier as a starting position to evaluate the cost of its neighbors, than a point with higher costs.
	The aggregation is implemented with early stopping. 
	After the last end point has been has got an aggregated cost the aggregation stops and the back tracking starts.

	\section{Methods}\label{sec:methods}

	\input{methods}

	\section{Results}\label{sec:results}

	\input{results}

	\section{Discussion}\label{sec:discussion}
	\input{discussion}

	\section{Related Works}\label{sec:related-works}

	\section{Conclusion}\label{sec:conclusion}
	When using the researched strategies, the on medium resolution raster, the computation for high resolution results might successfully be reduced, without compromising the run time for worse distances to the least cost path from the high resolution raster.
	\todo{Befragung: local population, relative weights per district?}

### 2023-02-19 paper/results.tex
added Supplement S1
paper:
results.tex:
added part for the sub-sections:
 1) for overlay of both rasterizations
 2) for down sampled cost paths

refactor: added discussion.tex
added citations, parts for the Introduction

update format of least_cost_path_evaluation.ipynb

In this chapter we want to show the different cost raster, that were created from the very same set of layers,
but computed for different resolutions.
From this different raster the cost paths are calculated and compared.
In the last step the raster with lower resolution were used to calculate in a way, that they shall result in
similar paths as if the paths were computed from a high resolution raster.
\subsection{Cost Raster}\label{subsec:cost-raster}

@@

The distance of both paths is calculated with the mean minimum distance.
For every vertex $P_i$ in the path $L_1$ the minimum between the vertex and the path $L_2$
is computed and afterwards the minimum distances are averaged (see equation~\ref{eq:1}).
\begin{equation}
	\label{eq:1}
	d_{mean} = \frac{1}{|L_1|} \sum_{i=1}^{n} d_{min}(p_i, L_2) \bigg\vert p_i \in L_1
\end{equation}

@@

At the same time the differences in the aggregated costs stay constant.
\todo{Interpretation} When normalize the aggregated costs by the resolution.
Than On one hand it can be seen, that the all\_touched False under estimate the costs and that this tendency scales
linear with the resolution.
On the other hand, the all\_touched True least cost over estimates the aggregated costs on a linear scale of
the resolution.
Therefore, the difference for the normalized least cost paths is reduced on scale by the resolution.\todo{show map}

@@

\begin{table*}[t]
	\caption{Least cost paths as length for the different \acrfull{res} of the raster, including the mean minimum distance and the maximum minimum distance and the \acrfull{agg.} costs. From the \acrshort{agg.} costs the differences of the \acrshort{agg.} costs and the \acrfull{corr} \acrshort{agg.} by resolution are given.} 
	\label{tab:2}
	\centering
	\begin{tabular}{ r  r  r  r  r  r  r  r  r  r}
		\acrshort{res} /m & $length_{\acrshort{al}=\acrshort{f}} /m$ & $length_{\acrshort{al}=\acrshort{t}} /m$ & $d_{mean}$ /m & $d_{max}/m$ & \acrshort{agg.}  $ cost_{\acrshort{al}=\acrshort{f}}$ & \acrshort{agg.}  $ cost_{\acrshort{al}=\acrshort{t}}$ &  $\Delta $ costs & \acrshort{corr} \acrshort{agg.} $costs_{\acrshort{al}=\acrshort{f}}$ & \acrshort{corr} \acrshort{agg.} $costs_{\acrshort{al}=\acrshort{t}} $ \\
		\hline
		5 	& 76136.27	& 78002.00 &  126.04 & 1065.00 & 18665.923 & 19616.756 & -850.00 & 93329.60 &  97584.77 \\
		10 	& 75430.10 	& 77936.57 &  277.92 & 1590.00 &  8931.245 &  9731.175 & -799.95 & 89312.45 &  97311.75 \\
		25 	& 75422.85 	& 78422.85 &  313.75 & 1621.15 &  3354.869 &  3872.656 & -517.78 & 83871.73 &  96816.40 \\
		50 	& 76135.02	& 70619,95 & 1140.01 & 4950.00 &  1409.023 &  2300.073 & -891.05 & 70451.15 & 115003.65 \\
		100 & 76283.80	& 74120.73 & 1946.41 & 6016.64 &   640.516 &  1572.268 & -931.70 & 64051.60 & 167226.80 \\

@@

The zonal stat (see table~\ref{tab:3}) for a buffer of 100 m (5 m) around the path has been used, to estimate the
percentage of which costs levels are around the path.
When using all\_touched True rasterization with higher resolution the tendency is to use a higher percentage of the
Preferential Level and less the NoRestriction Level.\todo{Interpretation:}
The ratio of the 100 m buffered least cost path, strongly shifted  to Levels lower costs.
\todo{Interpretation: Interpretation the Cost Paths are much nearer smaller, than 100 m! No problem because buffering is included in the cost raster.}
There is no strong tendency for the all\_touched False least cost paths.

\subsection{Execution time}\label{subsec:execution-time}
In theory, the execution time should increase with the square of the resolution, because higher resolutions result in a higher number of pixels and thus data points the aggregated costs needs to be calculated for. 
A full logarithmic fit for several repetitions of the execution shows, that the execution time scales with power of $2.1997  \pm 0.007$ of the inverse resolution. 
With the caveat of a low number of samples this can equally be success fully be fitted to a second degree polynomial of the inverse resolution with a $r^2$ for the test set of 0.99 and a the squared inverse of the resolution with a $r^2$ for the test set of 0.99.
Hence, the order of magnitude

The total execution time consists of two parts. 
The aggregation of the costs and the back tracking of the least cost to find the path.
\todo{back tacking scales with number of points.}

\todo{used regions}

@@

\begin{table*}[t]
	\caption{\acrfull{r} of Category percentages of each least cost path for a buff of 100 m (5 m) around the least cost path.}
	\label{tab:3}
	\centering
	\begin{tabular}{ r  r  r r  r r  r r  r r  r r}
		resolution /m & all touched & \multicolumn{2}{c}{ $ r_{Preferential} \% $}  & \multicolumn{2}{c}{ $ r_{No Restriction} \% $ }  & \multicolumn{2}{c}{ $ r_{Restricted} \% $}  & \multicolumn{2}{ c }{ $ r_{strongly Restricted}\% $ } & \multicolumn{2}{c}{ $ r_{Prohibited} \% $ } \\
		\hline
		5 & False &  4.7  &  (5.4) & 58.7 & (58.9) & 8.8 & (8.4) & 0.7 & (0.7) & 27.1 & (26.7)  \\
		10 & False &  19.6 & (33.5) & 68.5 & (64.5)  & 1.0 & (0.8) & 0.8 & (0.3) & 10.1 & (0.9)\\
		25 & False &  19.2 & (34.2) & 68.9 & (64.9)  & 1.0 & (0.2) & 0.7 & (0.1) & 9.7 & (0.6)\\
		50 & False &  20.4 & (33.2) & 68.0 & (66.2)  & 0.9 & (0.1) & 0.7 & (0.0) & 10.1 & (0.5)\\
		100 & False &  21.1 & (30.7) & 69.1 & (68.8)  & 1.1 & (0.0) & 0.7 & (0.0) & 7.9 & (0.4) \\

@@

The final least costs paths should between the least cost paths of the lower resolution, with a tendency to be nearer to the paths resulted by the all touched false rasterization.
The first step is to optimize the calculation speed is, only to calculated the least cost paths for this smaller area.
Another method, is to improve the prediction of the medium resolution itself and thus reduce the need for a computation in higher resolution.
\subsubsection{Compare least cost paths, for overlay of both rasterizations}
As all touched true rasterization overestimates and all touched true underestimates the real costs.
A weighted mean will describe the real costs more precise.
As present work indicates, that the weight should favor the all touched false raster.
The best weight should be the percentage of the pixel, which is covered by the object, but this can not be computed in this work.
Thus, the best weight has to be searched.
An alternative might be to compute the cost raster in higher resolution, but than to reproject the to a smaller resolution with a using a (linear) interpolation of the of the weights.

@@

\subsubsection{Compare least cost paths, for down sampled cost paths}
As an alternative to the super position of the all touched true and false raster for the same resolution, the all touched false raster was down sampled to 10~m, 25~m, 50~m and 100~m with bi-linear interpolation.
With this method smaller structures still can be seen in the cost raster, although the resolution is reduced.

% \subsubsection{Restrict search to a minimum sized bounding box}
\subsubsection{Restrict search to a buffered around the least cost paths}
Construct a polygon form the two lines.
Buffer the polygon with twice the max minimum path distance.

@@

\subsubsection{Restrict search to reachable points}
For this purpose the aggregated cost as to converted back into a raster.

\subsubsection{Compare the different Solutions}
\subsubsection{Check solution for least cost path between different points}

>>>>

In this chapter we want to show the different cost raster, that were created from the very same set of layers,
but computed for different resolutions.
From this different raster the cost paths are calculated and compared.
In the last step the raster with lower resolution were used to calculate in a way, that they shall result in
similar paths as if the paths were computed from a high resolution raster.

\subsection{Cost Raster}\label{subsec:cost-raster}

@@

The distance of both paths is calculated with the mean minimum distance.
For every vertex $P_i$ in the path $L_1$ the minimum between the vertex and the path $L_2$
is computed and afterwards the minimum distances are averaged (see equation~\ref{eq:1}).
\begin{equation}
	\label{eq:1}
	d_{mean} = \frac{1}{|L_1|} \sum_{i=1}^{n} d_{min}(p_i, L_2) \bigg\vert p_i \in L_1
\end{equation}
This equation is used, to measure the extent of similarity between the paths.

@@

At the same time the differences in the aggregated costs stay constant.
\todo{Interpretation} When normalize the aggregated costs by the resolution.
Than On one hand it can be seen, that the all\_touched False under estimate the costs and that this tendency scales
linear with the resolution.
On the other hand, the all\_touched True least cost over estimates the aggregated costs on a linear scale of
the resolution.
Therefore, the difference for the normalized least cost paths is reduced on scale by the resolution.

@@

\begin{table*}[t]
	\caption{Least cost paths as length for the different \acrfull{res} of the raster, including the mean minimum distance and the maximum minimum distance and the \acrfull{agg.} costs. From the \acrshort{agg.} costs the differences of the \acrshort{agg.} costs and the \acrfull{corr} \acrshort{agg.} by resolution are given.} 
	\label{tab:2}
	\centering
	\begin{tabular}{ r  r  r  r  r  r  r  r  r  r}
		\acrshort{res} /m & $l_{\acrshort{al}=\acrshort{f}} /m$ & $l_{\acrshort{al}=\acrshort{t}} /m$ & $d_{mean}$ /m & $d_{max}/m$ & \acrshort{agg.}  $ cost_{\acrshort{al}=\acrshort{f}}$ & \acrshort{agg.}  $ cost_{\acrshort{al}=\acrshort{t}}$ &  $\Delta $ costs & \acrshort{corr} \acrshort{agg.} $costs_{\acrshort{al}=\acrshort{f}}$ & \acrshort{corr} \acrshort{agg.} $costs_{\acrshort{al}=\acrshort{t}} $ \\
		\hline
		5 	& 76136.27	& 78002.00 &  126.04 & 1065.00 & 18665.923 & 19616.756 & -850.00 & 93329.60 &  97584.77 \\
		10 	& 75430.10 	& 77936.57 &  277.92 & 1590.00 &  8931.245 &  9731.175 & -799.95 & 89312.45 &  97311.75 \\
		25 	& 75422.85 	& 78422.85 &  313.75 & 1621.15 &  3354.869 &  3872.656 & -517.78 & 83871.73 &  96816.40 \\
		50 	& 76135.02	& 70619,95 & 1140.01 & 4950.00 &  1409.023 &  2300.073 & -891.05 & 70451.15 & 115003.65 \\
		100 & 76283.80	& 74120.73 & 1946.41 & 6016.64 &   640.516 &  1572.268 & -931.70 & 64051.60 & 167226.80 \\

@@

The zonal stat (see table~\ref{tab:3}) for a buffer of 100 m (5 m) around the path has been used, to estimate the
percentage of which costs levels are around the path.
When using all\_touched True rasterization with higher resolution the tendency is to use a higher percentage of the
Preferential Level and less the NoRestriction Level.\todo{Interpretation:}
The ratio of the 100 m buffered least cost path, strongly shifted  to Levels lower costs.

There is no strong tendency for the all\_touched False least cost paths.

\subsection{Execution time}\label{subsec:execution-time}

In theory, the execution time should increase with the square of the resolution, because higher resolutions result in a higher number of pixels and thus data points the aggregated costs needs to be calculated for. 
A full logarithmic fit for several repetitions of the execution shows, that the execution time scales with power of $2.1997  \pm 0.007$ of the inverse resolution. 
With the caveat of a low number of samples this can equally be success fully be fitted to a second degree polynomial of the inverse resolution with a $r^2$ for the test set of 0.99 and a the squared inverse of the resolution with a $r^2$ for the test set of 0.99.
Hence, the order of magnitude

The total execution time consists of two parts. 
The aggregation of the costs and the back tracking of the least cost to find the path.
% \todo{back tacking scales with number of points.}

@@

\begin{table*}[t]
	\caption{\acrfull{r} of Category percentages of each least cost path for a buff of 100 m (5 m) around the least cost path.}
	\label{tab:3}
	\centering
	\begin{tabular}{ r  r  r r  r r  r r  r r  r r}
		res /m & all touched & \multicolumn{2}{c}{ $ r_{Preferential} \% $}  & \multicolumn{2}{c}{ $ r_{No Restriction} \% $ }  & \multicolumn{2}{c}{ $ r_{Restricted} \% $}  & \multicolumn{2}{ c }{ $ r_{strongly Restricted}\% $ } & \multicolumn{2}{c}{ $ r_{Prohibited} \% $ } \\
		\hline
		5 & False &  4.7  &  (5.4) & 58.7 & (58.9) & 8.8 & (8.4) & 0.7 & (0.7) & 27.1 & (26.7)  \\
		10 & False &  19.6 & (33.5) & 68.5 & (64.5)  & 1.0 & (0.8) & 0.8 & (0.3) & 10.1 & (0.9)\\
		25 & False &  19.2 & (34.2) & 68.9 & (64.9)  & 1.0 & (0.2) & 0.7 & (0.1) & 9.7 & (0.6)\\
		50 & False &  20.4 & (33.2) & 68.0 & (66.2)  & 0.9 & (0.1) & 0.7 & (0.0) & 10.1 & (0.5)\\
		100 & False &  21.1 & (30.7) & 69.1 & (68.8)  & 1.1 & (0.0) & 0.7 & (0.0) & 7.9 & (0.4) \\

@@

The final least costs paths should between the least cost paths of the lower resolution, with a tendency to be nearer to the paths resulted by the all touched false rasterization.
The first step is to optimize the calculation speed is, only to calculated the least cost paths for this smaller area.
Another method, is to improve the prediction of the medium resolution itself and thus reduce the need for a computation in higher resolution.
\subsubsection{Compare least cost paths, for overlay of both rasterizations}

As all touched true rasterization overestimates and all touched true underestimates the real costs.
A weighted mean will describe the real costs more precise.
As present work indicates, that the weight should favor the all touched false raster.
The best weight should be the percentage of the pixel, which is covered by the object, but this can not be computed in this work.
Thus, the best weight has to be searched.
An alternative might be to compute the cost raster in higher resolution, but than to reproject the to a smaller resolution with a using a (linear) interpolation of the of the weights.

@@

The optimal ratio of overlaying all touched false and all touched true cost raster for 10~m resolution is estimated via the resulting least cost path. 
The mean distance of least cost paths for different ratio has been estimated to the path from the all touched false raster of the next higher (5~m) resolution. 
Table~\ref{tab:4} shows, that distance decreases with the higher ratio from 1:1, 2:1, 4:1 and than increases with higher ratio 8:1, 16:1 and so on.
In addition, the distances to the original paths from the all touched false and all touched true raster change with the applied ratio of the overlayed raster.
So that, a lower ratio increases the similarity to the path of the all touched true raster, the similarity to the paths from the all touched false raster increases with the ratio.

\begin{table}[h!]
	\caption{Length of the path computed from the overlaying of all touched false and true raster and the mean distance of the paths to the paths calculated from the all touched false 5~m resolution  and all touched false and true raster of 10~m resolution.}
	\label{tab:4}
	\centering
	\begin{tabular}{ r  r  r  r}
		r & $d_{5~al=f}$ /m &  $d_{10~al=f}$ /m & $d_{10~al=t}$ /m \\
		\hline

		  1:1  &    119.6 &  285.50 &  47.21\\
		  2:1  &    97.11 &  263.51 &  74.19\\
		  4:1  &    40.13 &  206.38 & 100.16\\
		  8:1  &    41.73 &  169.02 & 137.34\\
		 16:1  &    56.69 &  153.32 & 152.71\\
		 32:1  &    56.69 &  145.56 & 162.09\\
		 64:1  &   163.48 &   10.61 & 272.36\\
	  % 128:1  &   163.82 &   10.29 & 276.71\\

	\end{tabular}
\end{table}

\subsubsection{Compare least cost paths, for down sampled cost paths}

As an alternative to the super position of the all touched true and false raster for the same resolution, the all touched false raster was down sampled to 10~m, 25~m, 50~m and 100~m with bi-linear interpolation.
With this method smaller structures still can be seen in the cost raster, although the resolution is reduced.
The distances of the paths that are computed from the bi-linear down sampled  5~m resolution raster (all touched false) is from table~\ref{tab:5} shows, that a low distance to path of the 5~m resolution raster was only obtained when down sampling to a resolution not to low.
Only when down sampling to a resolution of 10~m, is the computed path considerable close to the path from the higher resolution raster.
Is holds true, but to a much reduced extend to the path computed from the raster, that was down sampled to a resolution of 25~m.
The opposite is true for the lower resolution raster which is more similar to paths computed from the all touched true cost raster.
For every path from a down sampled raster is more similar to a path computed from an all touched true raster, than an all touched false raster, although the all touched false raster of the 5 m resolution was used for down sampling.

\begin{table}[h!]
	\caption{Length of the path computed from the bi-linear down sampled raster and the mean distance of the paths from the down sampled raster to the paths calculated from the all touched true and all touched false raster of the same resolution as the down sampled raster.}
	\label{tab:5}
	\centering
	\begin{tabular}{ r  r  r  r  r}
		res /m & l /m  & $d_{5~m}$ /m &  $d_{al=f}$ /m & $d_{al=t}$ /m \\
		\hline

		10  & 75980.62 &   59.34 &  219.35 & 143.63\\
		25  & 70205.27 &  385.79 &  558.12 & 432.77\\
		50  & 69217.86 &  730.82 &  693.42 & 255.70\\
		100 & 66667.87 &  1681.3 & 1605.63 & 400.55\\

	\end{tabular}
\end{table}

% \subsubsection{Restrict search to a minimum sized bounding box}
\subsubsection{Restrict search to a buffered around the least cost paths}

Construct a polygon form the two lines.
Buffer the polygon with twice the max minimum path distance.

@@

%\subsubsection{Restrict search to reachable points}
%For this purpose the aggregated cost as to converted back into a raster.

\subsubsection{Check solution for least cost path between different points}
